### 2020-11-17 Thesis-Chapter4-Arguments.tex
Integrate koepke_2020 into arguments

\begin{figure}[p!]
  \centering\CaptionFontSize
  \includegraphics[width=0.9\linewidth]{arguments/build/comprehensive.goldenage.pdf}
  \caption{A ``Golden Age for Surveillance'' Argument Map}
  \label{fig-arg-golden-age}
\end{figure}

@@

The real change that this policy would take would be a sanctioning and formalization of this strategy. One downside is
that it would be of little use to ill-resourced departments, nullifying its usefulness for more commonplace crimes. Its
major downside is the altered relation is would create between law enforcement and tech companies. Instead of
cooperation, they are suddenly thrust into competition, with law enforcement incentivized to hoard rather than disclose
vulnerabilities it discovers. Prominent proposals suggest mandating prompt disclosure of discovered vulnerabilities
\cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}. Theoretically, the supply of vulnerabilities is very large,
and new ones could be found at a rate that maintains law enforcement access at constant levels while improving security
as a positive side effect. The government would source these vulnerabilities from a combination of the public domain,
the commercial exploit market, and a central ``Vulnerability Lab'' \cite{bellovin_lawful_2013}. However, as the \$2
million price on the exploit market for an Apple iOS jailbreak bug shows, security really is improving
\cite{goodin_zeroday_2019}. Law enforcement would still find itself without access, and would need to develop costly
exploits in the lab. Mandatory vulnerability disclosure is key to a \ac{lawful-hacking} proposal; however, based on the
\ac{FBI}'s historical abuses of power \cite{shamsi_2011} and Congress's distaste for funding even initiatives it has
passed \cite{keller_internet_2019} or providing strong oversight \cite{johnson_congressional_2004}, one cannot imagine
that the government would actually give up such expensive vulnerabilities so easily when they are the pillar of their
access strategy.

@@

>>>>

\begin{figure}[p!]
  \centering\CaptionFontSize
  \includegraphics[width=\linewidth]{arguments/build/comprehensive.goldenage.pdf}
  \caption{A ``Golden Age for Surveillance'' Argument Map}
  \label{fig-arg-golden-age}
\end{figure}

@@

The real change that this policy would take would be a sanctioning and formalization of this strategy. One downside is
that it would be of little use to ill-resourced departments, nullifying its usefulness for more commonplace crimes. Its
major downside is the altered relation is would create between law enforcement and tech companies. Instead of
cooperation, they are suddenly thrust into competition, with law enforcement incentivized to hoard rather than disclose
vulnerabilities it discovers. Prominent proposals suggest mandating prompt disclosure of discovered vulnerabilities
\cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}. Theoretically, the supply of vulnerabilities is very large,
and new ones could be found at a rate that maintains law enforcement access at constant levels while improving security
as a positive side effect. The government would source these vulnerabilities from a combination of the public domain,
the commercial exploit market, and a central ``Vulnerability Lab'' \cite{bellovin_lawful_2013}.

The availability and cost of exploits ebbs and flows. On one hand, January 2019 sported a \$2 million price on the
exploit market for an Apple iOS jailbreak bug \cite{goodin_zeroday_2019}. On the other hand, an October 2020 report
shows that law enforcement agencies can extract data from nearly every mobile phone on the market for less than \$2000 a
unit \cite{koepke_2020}. As the exploit arms race continues, exploitability will be inconsistent. In the end, law
enforcement would face periods where it struggles for access, and would need to develop costly exploits in the lab.
Mandatory vulnerability disclosure is key to a \ac{lawful-hacking} proposal; however, based on the \ac{FBI}'s historical
abuses of power \cite{shamsi_2011} and Congress's distaste for funding even initiatives it has passed
\cite{keller_internet_2019} or providing strong oversight \cite{johnson_congressional_2004}, one cannot imagine that the
government would actually give up expensive vulnerabilities easily when they are the pillar of their access strategy.

@@

% FIXME: add note about how device security actually totally sucks

### 2020-11-17 Thesis-Chapter6-PathsAhead.tex
Separate strategies and mapping chapters
Finish risk analysis
Clean up conclusion notes
Integrate koepke_2020 into arguments

In this chapter, describe actions to take in discussion, regulation, and research.

% Leave for conclusion chapter:
% Subject four: now what?
%  --> How current proposals stack up against desired properties, threat model
%  --> security expert? do research, provide clear security advice, be vigilant
%  --> policymaker? fund research, don't mislead, don't be premature
%  --> either? know that there is no stable solution, balance rules and principles, serve your neighbor
% see varia_2018

\section{Legislative Priorities}

\begin{itemize}
    \item Reject EA until technical capabilities are ready \cite{varia_2018}
    \item Be forthcoming with data so that we know what to work on \cite{devlin_2018}
    \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
        (e.g., ECPA became outdated because was too tied to specific technology \cite{shamsi_2011})
    \item Fund the research \cite{varia_2018} (like \cite{goss_hr2616_1999})
\end{itemize}

\section{Technical Research}

\begin{itemize}
    \item Acknowledge the moral character of cryptography \cite{rogaway_moral_2015}
    \item Do the research
    \item Focus on principles \cite{levy_robinson_2018}
    \item Be clear on definitions \cite{varia_2018}, but don't expect govt to provide those (unlike
            \cite{abelson_2015}), and clearly define their interfaces with principles
            \cite{matyas_incommensurability_2018}
\end{itemize}

% Address accountability suggestion: blockchains (goldwasser_public_2017)

>>>>

% We have a wicked problem
% I propose we handle it a certain way
% Part of this is cooperative debate, which I tried to capture in argument maps
% Another element is focusing on specific proposals, so we dove into LDAWMSR

%% Prof. Walsh:
%% The dynamic regulatory environment and competing governmental branches at the executive, legislative, and judicial
%% level will continue to shape the...

% What can we conclude?
%   - It may not feel like it, but (meaningful) debate and discussion counts as progress for a wicked problem
%   - Neither side has the whole picture, but the "no EA" arguments are currently stronger
%   - A threat model including malicious users and threatening governments makes EA make more sense
%   - Device escrow with secure hardware represents true progress towards acceptably secure EA, so hope is not lost
% Where do we go from here?
%   - This was an attempt an "OO" iteration in the OODA; we need more, with involvement all around
%   - committee_decrypting_2018 presented a framework to use to judge proposals. I have a simple version of it.
%     here are where we are weak:
%       - X
%       - Y
%       - Z
%   - Government:
%       - Take the low hanging fruit first, please
%       - Fund research, don't mislead, don't be premature
%           - If you're going to compare it to going to the moon, fund us like it!
%       - Take on weak area XYZ
%   - Tech:
%       - Do research, provide clear security advice, be vigilant
%       - Take on weak area XYZ
%   - Either:
%       - Know that there is no stable solution, balance rules and principles, serve your neighbor
% see varia_2018 (maybe a good quote?)

%%%%%%%%%%%%%%%%%%%%%%%%%
% OLD NOTES for reference
%%%%%%%%%%%%%%%%%%%%%%%%%

% In this chapter, describe actions to take in discussion, regulation, and research.

% \section{Legislative Priorities}

% \begin{itemize}
%     \item Reject EA until technical capabilities are ready \cite{varia_2018}
%     \item Be forthcoming with data so that we know what to work on \cite{devlin_2018}
%     \item Don't prescribe technical methods, but be clear about principles \cite{matyas_incommensurability_2018}
%         (e.g., ECPA became outdated because was too tied to specific technology \cite{shamsi_2011})
%     \item Fund the research \cite{varia_2018} (like \cite{goss_hr2616_1999})
% \end{itemize}

% \section{Technical Research}

% \begin{itemize}
%     \item Acknowledge the moral character of cryptography \cite{rogaway_moral_2015}
%     \item Do the research
%     \item Focus on principles \cite{levy_robinson_2018}
%     \item Be clear on definitions \cite{varia_2018}, but don't expect govt to provide those (unlike
%             \cite{abelson_2015}), and clearly define their interfaces with principles
%             \cite{matyas_incommensurability_2018}
% \end{itemize}
